Primary analyses

### 2025-06-30 analysis/primary_analyses.qmd
fix bold values in tbl-3

  flextable::bold(i = ~ age_age > 0.6, j = "age_age") |>
  flextable::bold(i = ~ age_Alter_realW > 0.6, j = "age_Alter_realW") |>
  flextable::bold(i = ~ age_Geschlecht > 0.6, j = "age_Geschlecht") |>
  flextable::bold(i = ~ height_height > 0.6, j = "height_height") |>
  flextable::bold(i = ~ height_Koerpergroesse_realW > 0.6, j = "height_Koerpergroesse_realW") |>
  flextable::bold(i = ~ height_Geschlecht > 0.6, j = "height_Geschlecht") |>
  flextable::bold(i = ~ weight_weight > 0.6, j = "weight_weight") |>
  flextable::bold(i = ~ weight_Koerpergewicht_realW > 0.6, j = "weight_Koerpergewicht_realW") |>
  flextable::bold(i = ~ weight_Geschlecht > 0.6, j = "weight_Geschlecht") |>

>>>>

  flextable::bold(i = ~ abs(parse_number(age_age)) > 0.6, j = "age_age") |>
  flextable::bold(i = ~ abs(parse_number(age_Alter_realW)) > 0.6, j = "age_Alter_realW") |>
  flextable::bold(i = ~ abs(parse_number(age_Geschlecht)) > 0.6, j = "age_Geschlecht") |>
  flextable::bold(i = ~ abs(parse_number(height_height)) > 0.6, j = "height_height") |>
  flextable::bold(i = ~ abs(parse_number(height_Koerpergroesse_realW)) > 0.6, j = "height_Koerpergroesse_realW") |>
  flextable::bold(i = ~ abs(parse_number(height_Geschlecht)) > 0.6, j = "height_Geschlecht") |>
  flextable::bold(i = ~ abs(parse_number(weight_weight)) > 0.6, j = "weight_weight") |>
  flextable::bold(i = ~ abs(parse_number(weight_Koerpergewicht_realW)) > 0.6, j = "weight_Koerpergewicht_realW") |>
  flextable::bold(i = ~ abs(parse_number(weight_Geschlecht)) > 0.6, j = "weight_Geschlecht") |>
